Semantic Textual Similarity using deep learning

### 2017-05-30 paper/main.tex
Added initial related work

\section{Second section}

In scientific papers, this section usually (but not necessarily) briefly describes the related research and what makes the presented approach different from it.

>>>>

\section{Related work}

STS has short and fruitful history, one with many ideas flying around. In its current form it appeared in 2012, on SemVal~\citep{agirre2012semeval} as task 6.  In 2012, the best system~\citep{bar2012ukp} used lexical similarity and Explicit Semantic Analysis(ESA)~\citep{gabrilovich2007computing}. Following year Latent Semantic Analysis(LSA)~\citep{deerwester1990indexing} model~\citep{han2013umbc} with additional external information sources, WordNet and n-gram matching technique.

Following two years~\citep{sultan2014dls} and~\citep{sultan2015dls} dominate the competition with new algorightm -- they align the words between new sentences. Other notable approaches come from logic side, it's representative paper being~\citep{beltagy2014probabilistic}.
